Zero-shot task adaptation by homoiconic meta-mapping

### 2019-11-11 writing/iclr2020_submission/rebuttal.txt

- Shared Z vs. Separate task embedding: reuse of M (or, H network) network will only be possible if the input and output dimensions are same - i.e. the dimension of Z_output of M is the same as the dimension of Z_input of the M. What if  input and output dimensions are not the same?

Because Z is a latent space, we can choose its dimensionality however we wish, so we can choose for those embeddings to be the same. If we have pre-trained encoders we would like to use, we can either choose a latent the same size as their output, or map their latents into Z with an additional layer.

Other minor comments:

* One general comment is: please mention the “Zero-shot” experiments more clearly (may be a separate paragraph or subsection), otherwise it is hard to follow.
    Thanks, we have noted the sections and clarified this in the figure captions.
* Figure 2(a) please remove the question mark (?) after Held-out. Similarly, Figure 5: Please complete the sentence “ Performing from …”. 
    Done.
* Figure 1: (a)  Basic meta-learning: Please use some other color to highlight “(a)  Basic meta-learning”, the grey gives an illusion that the step ((a)  Basic meta-learning is not important.
    We chose this color because our main contribution is about meta-mapping, not meta-learning, so we wanted to highlight the latter panels.
* A term such as “Homoiconic” would have benefited from a formal definition, especially considering it’s not a commonly used term.
    There are debates about how to precisely define this term (see e.g. https://www.expressionsofchange.org/dont-say-homoiconic/), so we didn't want to wade into such a definitional conundrum. However, we provide a statement of the general agreed-upon part of the definition in the introduction.
* The presentation is in general not well-polished, and needs revision.
    Are there specific points that would benefit from further clarification, beyond what you have mentioned above?

@@

> No comparisons were provided to any baselines/alternative methods.

We do compare to a number of lesions in the supplement, and to an alternative method (performing tasks from a description alone). We have moved this latter comparison to the main text at the suggestion of Reviewer 1.

> in Sections 4 and 5 I was hoping to see comparisons to methods like MAML. Also, I felt that the proposed approach in Section 5 is very similar to MAML intuitively. This makes a comparison with MAML even more desirable. Without any comparisons it’s hard to tell how difficult the tasks under consideration are and what would amount to good performance on the held-out tasks.

Our main contribution is to propose a meta-mapping framework for zero-shot task performance, and parsimonious method for performing these meta-mappings. MAML as such is not a method of zero-shot task performance, it requires examples to learn from. We could therefore compare to MAML for our basic-meta-learning results, but those are simply a sanity check. We also compare to a variety of baselines, including chance and optimal performance, untransformed representations, and the most correlated task experienced (in the cards domain). However, if our paper is accepted, and you feel that the comparison to MAML for basic meta-learning is useful, we will run MAML on our tasks before the camera-ready submission.

@@

> Also, the work by Platanios, et al. on contextual parameter generation is very relevant to this work as it tackles multi-task learning using HyperNetworks. It may be worth adding a short discussion/comparison to that work as it also considers zero-shot learning.

Thanks, we weren't familiar with this very interesting work! We have added a reference and a brief discussion of the relationship.

- Capitalize: “section” -> “Section”, “appendix” -> “Appendix”, “fig.” -> “Figure”. Sometimes these are capitalized, but the use is inconsistent throughout the paper.
    Thanks for pointing this out, fixed.
- “Hold-out” vs “held-out”. Be consistent and use “held-out” throughout.
    We are making a grammatical distinction here -- "held-out" is an adjective and "hold-out" is a noun. That is, one might refer to a "held-out task" or to a "a hold-out." Hopefully this clarifies things.

We hope that this clarifies things, and will help to address your concerns. Please let us know if further changes would be useful.

@@

Reviewer 3:

Thank you for the thorough and thoughtful review. We appreciate that you think our work is tackling zero-shot adaptation in an innovative way! We have made substantial revisions to try to clarify the presentation. We respond to some of your comments inline below.

- The major concern for this work is its lack of discussion and comparison with state-of-the-art meta-learning baselines. 
    o	In fact, the meta-mapping this work learns is the relationship between tasks, and the meta-task the authors mentioned is a group of tasks. In this sense, I strongly suggest the authors to go through the recent work [1], and compare with it. Even the datasets constructed in that paper can be used as a benchmark to validate the proposed method in image classification.
We agree that the approach proposed there is very interesting, and have added a brief discussion of it! However, it does not consider the types of systematic relationships between tasks to which our system applies. For example, switching from winning to losing one of card games results in exactly opposite strategies, while other meta-mappings denote other types of relationships (such as switching what suit is more valuable). Hierarchical clustering cannot capture these richly structure relationships (see e.g. McClelland, Sadeghi, and Saxe (2017), "A Critique of Pure Hierarchy: Uncovering Cross-Cutting Structure in a Natural Dataset"), and hierarchically clustered or similarity based datasets alone thus do not suffice. This is part of why we suggest the construction of new datasets in the future directions.

    o	Other basic meta-learning algorithms like MAML[3] and many others should still be compared and discussed, especially in the basic meta-learning setting in Figure 2.
Our main contribution is to propose a meta-mapping framework for zero-shot task performance, and parsimonious method for performing these meta-mappings. MAML as such is not a method of zero-shot task performance, it requires examples to learn from. We could therefore compare to MAML for our basic-meta-learning results, but those are simply a sanity check. We also compare to a variety of baselines, including chance and optimal performance, untransformed representations, and the most correlated task experienced (in the cards domain). However, if our paper is accepted, and you feel that the comparison to MAML for basic meta-learning is useful, we will run MAML on our tasks before the camera-ready submission.

@@

o More recent work on explicitly learning the embedding of a task should be noted and compared, including [1][2]. The meta-mapping in this work is still based on embedding of a task, i.e., z_func, which is obtained by the function network. So is it possible to replace the embedding with recent SOTA algorithms?

Thanks for the useful and interesting references! We believe that it might be possible to replace our method for generating task embeddings with another algorithm. We have added a reference, and we do mention some other methods for constructing function embeddings (last paragraph of the related work).

- Many important details and ablation studies are missing, making the work less convincing.
    We do include a number of ablation studies in Appendix E.

`
o Why don’t merge the results Fig. 2 and Fig. 3 and compare them in a single figure, so that the contribution of meta-mappings can be shown. 
    We think this would be extremely misleading, since fig. 2 is meta-learning (viz. performing tasks from examples), while figure 3 is performing tasks zero-shot, without examples. We have tried to edit the captions to clarify this. We have also moved figure 5. to the main text, which does include this comparison between performing a task zero-shot and from examples, as well as another baseline.

### 2019-11-11 writing/homoiconic_meta_mapping_main.tex
Iclr revision version
Tweaks for rebuttal

\PassOptionsToPackage{numbers}{natbib}

\usepackage[final]{neurips_2019}
%\usepackage{iclr2020_conference,times}

@@

\begin{abstract}
How can deep learning systems flexibly reuse their knowledge? Toward this goal, we propose a new class of challenges, and a class of architectures that can solve them. The challenges are meta-mappings, which involve systematically transforming task behaviors to adapt to new tasks zero-shot. The key to achieving these challenges is representing the task being performed in such a way that this task representation is itself transformable. We therefore draw inspiration from functional programming and recent work in meta-learning to propose a class of Homoiconic Meta-Mapping (HoMM) approaches that represent data points and tasks in a shared latent space, and learn to infer transformations of that space. HoMM approaches can be applied to any type of machine learning task, including supervised learning and reinforcement learning. We demonstrate the utility of this perspective by exhibiting zero-shot remapping of behavior to adapt to new tasks.
\end{abstract}

@@

\subsubsection*{Acknowledgements}
We would like to acknowledge Noah Goodman, Surya Ganguli, Katherine Hermann, Erin Bennett, and Arianna Yuan for stimulating questions and suggestions on this project.

>>>>

%\PassOptionsToPackage{numbers}{natbib}

%\usepackage[final]{neurips_2019}
\usepackage{iclr2020_conference,times}

@@

\begin{abstract}
How can deep learning systems flexibly reuse their knowledge? Toward this goal, we propose a new class of challenges, and a class of architectures that can solve them. The challenges are meta-mappings, which involve systematically transforming task behaviors to adapt to new tasks zero-shot. The key to achieving these challenges is representing the task being performed in such a way that this task representation is itself transformable. We therefore draw inspiration from functional programming and recent work in meta-learning to propose a class of Homoiconic Meta-Mapping (HoMM) approaches that represent data points and tasks in a shared latent space, and learn to infer transformations of that space. HoMM approaches can be applied to any type of machine learning task. We demonstrate the utility of this perspective by exhibiting zero-shot remapping of behavior to adapt to new tasks.
\end{abstract}

@@

%\subsubsection*{Acknowledgements}
%We would like to acknowledge Noah Goodman, Surya Ganguli, Katherine Hermann, Erin Bennett, and Arianna Yuan for stimulating questions and suggestions on this project.
